### 2011-04-06 msm2ca.tex
Commit because I can.
Finished subspaces.

	\subsection{Vector subspaces}
	\begin{defn}
		Let $V$ be a vector space defined over the field of scalars $\mathbb{F}$ and $U \subset V$, $U$ is subspace if it is a vector space over $\mathbb{F}$ for the operations inherited from $V$. 
		To be a subspace $U$ must
		\begin{itemize}
			\item Contain the zero vector 0
			\item Closed with respect to addition
			\item Closed with respect to multiplication
			\item Closed with respect to taking negative vectors
		\end{itemize}
	\end{defn}

@@

\section{Bases and dimension}
\section{Linear mappings}
\section{Isomorphisms}
\section{Matrix of linear mapping}
\section{Linear transformations}
\section{Eigenvectors}

>>>>

	\subsection{Vector subspaces}
	\begin{defn}
		Let $V$ be a vector space defined over the field of scalars $\mathbb{F}$ and $U \subset V$, $U$ is subspace if it is a vector space over $\mathbb{F}$ for the operations inherited from $V$. 
		To be a subspace $U$ must
		\begin{itemize}
			\item Contain the zero vector $0$
			\item Closed with respect to addition
			\item Closed with respect to multiplication
			\item Closed with respect to taking negative vectors
		\end{itemize}
	\end{defn}

@@

	\subsection{Subspace spanned by a set of vectors}
	\begin{thm}
		Suppose $X$ is a set of vectors from a vector space $V$. The subspace spanned by $X$ is the smallest subspace $W$ of $V$ containing $X$. We write that $W = \left< X \right>$.
	\end{thm}

	\subsection{Linear combinations}
	\begin{defn}
		A linear combination of the vectors from $X$ is an expression of the form $w = \sum_{i \in I} a_i u_i$ where $a_i \in \mathbb{F}$ (scalars) and $u_i \in X$ (vectors).
		If the set $X$ is infinite, them only finitely many $a_i$ are allowed to be nonzero. $w$ will of course be a vector, referred to as a linear combination of the $u_i$'s.
	\end{defn}

	\subsection{Subspace spanned by vectors}
	\begin{thm}
		Suppose $V$ is a vector space over $\mathbb{F}$, and $X = \{ u_i | i \in I \}$ is a set of vectors in $V$. Then $W=\left< X \right>$ consists of all vectors $w$ that are linear
		combinations of the vectors from $X$.
	\end{thm}

	\subsection{Is a vector in the subspace?}
	From above theorem, to check a given vector is contained in the subspace $W=\left< X \right>$, just check $w$ is a linear combination of the vectors $u_i$ from $X$.

\section{Bases and dimension}
	\begin{defn}
	\end{defn}

\section{Linear mappings}
\section{Isomorphisms}
\section{Matrix of linear mapping}
\section{Linear transformations}
\section{Eigenvectors}
